### 2017-03-23 ResearchNotes/stat_exps.tex

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_0_CTE-UMCED-2_all}
        \label{subfig:stat_004_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_3_INF7194_2_all}
        \label{subfig:stat_004_3_all}
    \end{subfigure}

    \caption
        [Stat 004 plots for all activities]
        {Stat 004 plots for all activities.}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_0_CTE-UMCED-2_cud}
        \label{subfig:stat_004_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_3_INF7194_2_cud}
        \label{subfig:stat_004_3_cud}
    \end{subfigure}

    \caption
        [Stat 004 plots for C, U, and D activities]
        {Stat 004 plots for C, U, and D activities.}

>>>>

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_most_0_CTE-UMCED-2_all}
        \label{subfig:stat_004_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_most_1_eDocOn-T1_all}
        \label{subfig:stat_004_3_all}
    \end{subfigure}

    \caption
        [Number of CRUD activities for two courses with greater activity]
        {Number of CRUD activities for two courses with greater activity.}

@@

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_most_0_CTE-UMCED-2_cud}
        \label{subfig:stat_004_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_most_1_eDocOn-T1_cud}
        \label{subfig:stat_004_3_cud}
    \end{subfigure}

    \caption
        [Number of Create, Update, and Delete activities for two courses with
        greater activity]
        {Number of Create, Update, and Delete activities for two courses with
        greater activity.}
